Experiment 2 of 4

### 2016-09-27 experiments/e2/writeup/e2.Rmd
tried to resize plots better for latex special issue

```{r rtplot, fig.width=5, fig.height=3, echo=F}
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=':', rtdataplot1$Number, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_log, x=Item, ymin=RT_log-ci, ymax=RT_log+ci,
                group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=3, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Number) 
rtplot
```

```{r blplot, fig.width=5, fig.height=2.5, echo=F}
bldata$Condition <- as.factor(paste(sep=':', bldata$Vagueness, bldata$Number))
bldata$response_category <- relevel(bldata$response_category, ref = 'expected')
blplot=ggplot(bldata) + 
  geom_bar(aes(Vagueness, fill=response_category), position = 'dodge') +
  #geom_errorbar() +
  facet_wrap(nrow=1,~Number) +
  scale_fill_grey(name="Response Type") +
  xlab(" ") +
  ggtitle("Response Type") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        plot.background=element_rect(fill=NA, color='white'))
blplot
```

>>>>

```{r rtplot, fig.width=5, fig.height=3, echo=F}
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=':', rtdataplot1$Number, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_log, x=Item, ymin=RT_log-ci, ymax=RT_log+ci,
                group=Condition, fill=Vagueness)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(pch=21, size=3, position=dodge) +
  #scale_shape_manual("",values = c(22, 22)) +
  scale_fill_manual("",values=c("black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), legend.position="top",
        aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Number)
rtplot
```

```{r blplot, fig.width=5, fig.height=2.5, echo=F}
bldata$Condition <- as.factor(paste(sep=':', bldata$Vagueness, bldata$Number))
bldata$response_category <- relevel(bldata$response_category, ref = 'expected')
blplot=ggplot(bldata) + 
  geom_bar(aes(Vagueness, fill=response_category), position = 'dodge') +
  #geom_errorbar() +
  facet_wrap(nrow=1,~Number) +
  scale_fill_grey(name="") +
  xlab(" ") +
  ggtitle("Response Type") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), legend.position="top", aspect.ratio=1,
        plot.background=element_rect(fill=NA, color='white'))
blplot
```
